### 2019-07-31 paper_06_milestone/1st/article.tex
Paper 6 compiles

to be the buoyancy Reynolds number, $ {\cal{R}} $, and a turbulent Froude
number, $ F_h $, defined as \begin{equation} {\cal{R}} = \frac{\epsilon_K}{\nu

@@

$ {\cal{R}} $ instead of $ Re $ has a clear advantage in the limit of strong
stratification, where $ {\cal{R}} $ may become very small, while $ Re $ still

@@

in flows with $ {\cal{R}} $ of the order of unity and smaller. Therefore, $
\Gamma $ will go to zero in the limit of small $ {\cal{R}} $, even though $ Re
$ may be large. On the other hand, it can be argued that the use of $ {\cal{R}}

@@

that $ \Gamma $ goes to zero as $ {\cal{R}} ^{-1/2} $ in the limit of large $
{\cal{R}} $, a hypothesis which has been widely referenced

@@

of $ {\cal{R}} $ using data from a tank experiments of grid generated

@@

{\cal{R}}^{-2/3} $ for large $ {\cal{R}} $. The problem with such

@@

{\cal{R}} $ is likely to be an effect of weak stratification (large $ F_h $)

@@

Reynolds numbers, suggesting that $ \Gamma $ should not vary with $ {\cal{R}} $

@@

The regime of strongly stratified turbulence, in which $ F_h $ is small and $
{\cal{R}} $ is large, is highly relevant for applications in the
ocean\cite[]{RileyDeBruynKops2003, Lindborg2006}, but is notoriously difficult
to reproduce in experiments and simulations. In trying to reach the strongly
stratified regime experimentally by increasing the degree of stratification,
the buoyancy Reynolds number often becomes so low that turbulence is totally
surpressed. Observations made in this regime suggest that $ \Gamma $ is
generally very small. Ivey \& Imberger \cite{IveyImberger1991} plotted mixing
efficiency derived from different laboratory measurements
\cite{Stillinger1983, Itsweire1986, Rohr1988, Lienhard1990} against a turbulent Froude
number. In the limit of large Froude number, the $ F_h^{-2} $-dependence is
clearly visible in all plots. At Froude number of the order of unity the
measurements indicate that $ \Gamma \approx 0.2 $, while at lower Froude
numbers, $ \Gamma $, or the related Richardson flux coefficient [Osborn], is
rapidly dropping below unity. In all likelihood, such observations are
artefacts of the limitation which is present in all observational studies of
strongly stratified turbulence, namely the severe difficulty in reaching the
regime where $ F_h $ is small while $ {\cal{R}} $ still is above a certain
limit. In the present study, we make an effort to push the limits further and
measure the mixing coefficient in a parameter regime which previously has not
been reached in laboratory studies. In particular, we focus on the regime, $ 10
< {\cal R} < 200 $, with $ F_h $ being as small as possible.

@@

\begin{figure}
\includegraphics[width=\figwidth]{tmp/fig_scheme_mixing}
\caption{Scheme representing the effect of mixing on the density profile and the center of mass.}
\label{fig:average:mixing}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=80mm]{../figs/scheme_milestone17}\\[5mm]
\includegraphics[width=80mm]{../figs/milestone17_top}
% \includegraphics[width=\figwidth]{../figs/real_setup_milestone}
\includegraphics[width=80mm]{tmp/fig_movement_carriage}

@@

\input{tmp/table.tex}

@@

\input{sec_open_science.latex}
% An interesting particularity of the MILESTONE experiment is to be based on
% open-source method and to provide open datasets and open-source packages to
% load and analyze them.
%
% Two open-source Python packages called FluidLab and FluidCoriolis
% \cite{fluiddyn} were developed for these experiments and used to control most
% of the objects during the experiments.
%
% For example the movement of the carriage and of the probes are controlled with
% a graphical application and Python scripts provided by fluidlab and
% FluidCoriolis. Horizontal scanning PIV is also made possible by controling the
% rotating mirror and the triggers of the camera by functions provided in
% fluidlab. This allows anyone to perform horizontal scanning PIV with a good
% camera (here a PCO Edge), a rotating mirror and a quite cheap acquisition board
% (T7 LabJack) to trigger the camera.
%
% FluidLab is a generic API for orchestrating laboratory experiments. The
% software leverages the object-oriented programming features in Python to model
% real life instrumentation. An experiment in the simplest level can be thought
% of as a network of interconnected instruments awaiting commands and also
% sending and receiving data.
%
% The computation of PIV fields is performed on the cluster of the LEGI with an
% open-source Python package called fluidimage
%
% Data processing and data opening with FluidCoriolis.

@@

\begin{figure}
\includegraphics[width=80mm]{tmp/fig_energy_vs_time}
\label{fig:energy:vs:time}

@@

\begin{figure}
\includegraphics[width=80mm]{tmp/fig_fit_EK}
\label{fig:fit:EK}

@@

\begin{figure}
\includegraphics[width=\figwidth]{tmp/fig_R_vs_Fh}
\label{fig:RvsFh}

@@

\begin{figure}
\includegraphics[width=\figwidth]{tmp/fig_R_vs_Fh_other_studies_with_milestone17}
\label{fig:RvsFh:other}

@@

\begin{figure}
\includegraphics[width=\figwidth]{tmp/fig_rho_vs_time}\\
\includegraphics[width=\figwidth]{tmp/fig_rho_vs_time_corrected}
\label{fig:rho:vs:time}

@@

\begin{figure}
\includegraphics[width=\figwidth]{tmp/fig_profiles_mixing}\\
\includegraphics[width=\figwidth]{tmp/fig_profiles_probe_averaged}
\label{fig:profiles:mixing}

@@

\begin{figure}
\includegraphics[width=\figwidth]{tmp/fig_energy_pot_vs_time}
\label{fig:energy:pot:vs:time}

@@

\begin{figure}
\includegraphics[width=\figwidth]{tmp/fig_dt_pot_energy}
\label{fig:dt:pot:energy}

>>>>

to be the buoyancy Reynolds number, $ {\mathcal{R}} $, and a turbulent Froude
number, $ F_h $, defined as \begin{equation} {\mathcal{R}} = \frac{\epsilon_K}{\nu

@@

$ {\mathcal{R}} $ instead of $ Re $ has a clear advantage in the limit of strong
stratification, where $ {\mathcal{R}} $ may become very small, while $ Re $ still

@@

in flows with $ {\mathcal{R}} $ of the order of unity and smaller. Therefore, $
\Gamma $ will go to zero in the limit of small $ {\mathcal{R}} $, even though $ Re
$ may be large. On the other hand, it can be argued that the use of $ {\mathcal{R}}

@@

that $ \Gamma $ goes to zero as $ {\mathcal{R}} ^{-1/2} $ in the limit of large $
{\mathcal{R}} $, a hypothesis which has been widely referenced

@@

of $ {\mathcal{R}} $ using data from a tank experiments of grid generated

@@

{\mathcal{R}}^{-2/3} $ for large $ {\mathcal{R}} $. The problem with such

@@

{\mathcal{R}} $ is likely to be an effect of weak stratification (large $ F_h $)

@@

Reynolds numbers, suggesting that $ \Gamma $ should not vary with $ {\mathcal{R}} $

@@

The regime of strongly stratified turbulence, in which $ F_h $ is small and $
{\mathcal{R}} $ is large, is highly relevant for applications in the
ocean\cite[]{RileyDeBruynKops2003, Lindborg2006}, but is notoriously difficult
to reproduce in experiments and simulations. In trying to reach the strongly
stratified regime experimentally by increasing the degree of stratification,
the buoyancy Reynolds number often becomes so low that turbulence is totally
surpressed. Observations made in this regime suggest that $ \Gamma $ is
generally very small. Ivey \& Imberger \cite{IveyImberger1991} plotted mixing
efficiency derived from different laboratory measurements
\cite{Stillinger1983, Itsweire1986, Rohr1988, Lienhard1990} against a turbulent Froude
number. In the limit of large Froude number, the $ F_h^{-2} $-dependence is
clearly visible in all plots. At Froude number of the order of unity the
measurements indicate that $ \Gamma \approx 0.2 $, while at lower Froude
numbers, $ \Gamma $, or the related Richardson flux coefficient [Osborn], is
rapidly dropping below unity. In all likelihood, such observations are
artefacts of the limitation which is present in all observational studies of
strongly stratified turbulence, namely the severe difficulty in reaching the
regime where $ F_h $ is small while $ {\mathcal{R}} $ still is above a certain
limit. In the present study, we make an effort to push the limits further and
measure the mixing coefficient in a parameter regime which previously has not
been reached in laboratory studies. In particular, we focus on the regime, $ 10
< \mathcal{R} < 200 $, with $ F_h $ being as small as possible.

@@

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_scheme_mixing}
\caption{Scheme representing the effect of mixing on the density profile and the center of mass.}
\label{fig:average:mixing}
\end{figure}

@@

\begin{figure}[htp!]
\centering
\includegraphics[width=80mm]{../figs/scheme_milestone17}\\[5mm]
\includegraphics[width=80mm]{../figs/milestone17_top}
% \includegraphics[width=\figwidth]{../figs/real_setup_milestone}
\includegraphics[width=80mm]{tmp/fig_movement_carriage}

@@

\input{paper_06_milestone/1st/tmp/table.tex}

@@

\input{paper_06_milestone/1st/sec_open_science.latex}
% An interesting particularity of the MILESTONE experiment is to be based on
% open-source method and to provide open datasets and open-source packages to
% load and analyze them.
%
% Two open-source Python packages called FluidLab and FluidCoriolis
% \cite{fluiddyn} were developed for these experiments and used to control most
% of the objects during the experiments.
%
% For example the movement of the carriage and of the probes are controlled with
% a graphical application and Python scripts provided by fluidlab and
% FluidCoriolis. Horizontal scanning PIV is also made possible by controling the
% rotating mirror and the triggers of the camera by functions provided in
% fluidlab. This allows anyone to perform horizontal scanning PIV with a good
% camera (here a PCO Edge), a rotating mirror and a quite cheap acquisition board
% (T7 LabJack) to trigger the camera.
%
% FluidLab is a generic API for orchestrating laboratory experiments. The
% software leverages the object-oriented programming features in Python to model
% real life instrumentation. An experiment in the simplest level can be thought
% of as a network of interconnected instruments awaiting commands and also
% sending and receiving data.
%
% The computation of PIV fields is performed on the cluster of the LEGI with an
% open-source Python package called fluidimage
%
% Data processing and data opening with FluidCoriolis.

@@

\begin{figure}[htp!]
\includegraphics[width=80mm]{tmp/fig_energy_vs_time}
\label{fig:energy:vs:time}

@@

\begin{figure}[htp!]
\includegraphics[width=80mm]{tmp/fig_fit_EK}
\label{fig:fit:EK}

@@

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_R_vs_Fh}
\label{fig:RvsFh}

@@

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_R_vs_Fh_other_studies_with_milestone17}
\label{fig:RvsFh:other}

@@

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_rho_vs_time}\\
\includegraphics[width=\figwidth]{tmp/fig_rho_vs_time_corrected}
\label{fig:rho:vs:time}

@@

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_profiles_mixing}\\
\includegraphics[width=\figwidth]{tmp/fig_profiles_probe_averaged}
\label{fig:profiles:mixing}

@@

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_energy_pot_vs_time}
\label{fig:energy:pot:vs:time}

@@

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_dt_pot_energy}
\label{fig:dt:pot:energy}
